article title

### 2022-07-23 pilon_gilles_glossary.tex
Add outlier
Add type I error

@@

>>>>

\newglossaryentry{outlier}
    name={outlier},
    description={It is a data point that differs significantly from other observations. An outlier may be due to variability in the measurement or it may indicate experimental error. An outlier can cause serious problems in statistical analyses.},
    plural={outliers}

@@

\newglossaryentry(type_i_error},
    name={type I error},
    description={It is the probability of saying something is different when in fact it is not. We find a difference that isn’t really there. It is also called alpha risk, producer's risk, and false positive.},
    plural={Type I errors}
